Dynamic Transition Analysis with TIMES

### 2019-01-24 doc/2019-02-presentation/assums.tex
moved cost plot to assumptions
minor punctuation corrections, added scenario frame title
Former-commit-id: 9e89b78dcdf4c533730cf1c055de182db6beb53b [formerly 20d17d0febcd06be3f506b362ab97d808910e4cf]
Former-commit-id: 02093b75aa75bd3201815b77b46f7e57b644889c
added authors

  \item New Nuclear = ABWRs

  \item Nuclear, wind, solar growth rates based on trends in USA, China, Japan.

@@

@@

>>>>

  \item New Nuclear = Advanced Boiling Water Reactors.

  \item Simplistic, conservative assumption about demand growth = +1.7\% per year.

  \item Nuclear, wind, solar annual growth rate \textbf{limits} based on trends in USA, China, Japan.

@@

  \item Offshore and onshore wind capacity limited to theoretical potential (about 450 GW and 200 GW respectively).

@@

\begin{frame}
  \frametitle{Levelized cost projections for solar and wind}
  \begin{figure}[htbp!]
    \begin{center}
      \includegraphics[scale=0.6]{./images/cost}
    \end{center}
          \caption{Cost variation of solar, wind, and H$_2$ production.}
    \label{cost}
  \end{figure}
\end{frame}

### 2019-01-24 doc/2019-02-presentation/motivation.tex
added Japan, institute name
Former-commit-id: e4906c7fec5c01ddbc3e6d1ee62d31cd55d4eb8d [formerly c43586cb782ac88d17c8683be43789b1d61fef85]
Former-commit-id: 53f869447949beeabf2da0cc26d732ed8d2ff031
added authors

   \item Dynamic transition analysis to minimize CO$_2$ emissions.

@@

   \item Emissions reduced by 80\% from 1990 levels by 2050, held constant until 2100 if possible.

>>>>

   \item Dynamic transition analysis to minimize CO$_2$ emissions in Japan.

@@

   \item \textbf{I$^2$CNER goal:} Reduce emissions by 80\% from 1990 levels by 2050,

   \item After 2050: emissions held constant until 2100 if possible.
